Transformation of forecasts for evaluating predictive performance in an epidemiological context

### 2023-05-07 reply_to_reviews.tex

\blue
Figure 5 caption:
\begin{itemize}
    \item “logarithmic” — With what a values? (THe first link to Figure 5 is from before this information was stated.)
    \item “D: [. . . ] all individual scores” — of EuroCOVIDhub-ensemble or any of the 7 included systems?
    \item “relative change” — of what change in scores relative to what quantity?
\end{itemize}

\black
We have updated the caption, which now reads:

\textit{Scores for two-week-ahead forecasts from the EuroCOVIDhub-ensemble (averaged across all forecast dates) for different locations, evaluated on the natural scale as well as after transforming counts by adding one and applying the natural logarithm. D: Corresponding boxplots of all individual scores of the EuroCOVIDhub-ensemble for two-week-ahead predictions. E: Boxplots for the relative change of scores for the EuroCOVIDhub-ensemble across forecast horizons. For any given forecast date and location, forecasts were made for four different forecast horizons, resulting in four scores. All scores were divided by the score for forecast horizon one. To enhance interpretability, the range of visible relative changes in scores (relative to horizon = 1) was restricted to [0.1, 10].}

\red

@@

L272: “with the standard deviation” — Also note here that this is for approximately normal data distributions?

\black 
The statement that the CRPS/WIS scales with the standard deviation is true in general. I think they have a point though that the beta = 1 etc. kind of assumes a normal distribution which we say is approximated well?

\blue
L282: “independent” — Consider “linearly independent”.

\black
We changed the sentence accordingly. ANY OBJECTIONS?

\red
L288–290: What would stakeholders want this difference to be, and in
which direction? I would guess the sqrt would generally be preferable unless applying some extra transformation after the log to re-emphasize locations/times of interest.

\black
That likely depends on the exact purpose stakeholders have in mind. In many instances it is presumably not desirable to give large weight to smaller forecast targets, and one may therefore e.g. choose to use the sqrt transformation or a different one over the log transformation. On the other hand, in our example the log transformation only gives a little bit more weight to smaller forecast targets, which may be acceptable given that the log transformation has nice properties in terms of its interpretation in an epidemiological context.

Do we need to make changes to the text?

\blue
Figure 7 caption: “one score” — Consider clarifying that/whether there is potentially missingness here.

\black
We have updated the Figure caption to make it more easily understandable. It now reads:

\textit{Correlations of rankings on the natural and logarithmic scale. A: Average Spearman rank correlation of scores for individual forecasts. For every individual target (defined by a combination of forecast date, target type, horizon, location), one score was obtained per model. Then, for every forecast target, the Spearman rank correlation was computed between scores on the natural scale and on the log scale for all the models that had made a forecast for that specific target. These individual rank correlations were then averaged across locations and time and are displayed stratified by horizon and target types, representing average accordance of model ranks for a single forecast target on the natural and on the log scale. B: Correlation between relative skill scores. For every forecast horizon and target type, a separate relative skill score was computed per model using pairwise comparisons, which is a measure of performance of a model relative to the others for a given horizon and target type that accounts for missing values. The plot shows the correlation between the relative skill scores on the natural vs. on the log scale, representing accordance of overall model performance as judged by scores on the natural and on the log scale.}

\blue
Figure 8: What is the meaning of the arrow colors? Initially it seems to match the direction, but there is also blue arrow pointing downward. If it is indicating the direction, please fix this and consider a third color for indicating unchanged ranks.

\black
The colour of the error indicates whether or not relative skill scores improved or deteriorated. We agree this was at all clear and thank you for pointing this out. We updated the plot legend and added a more detailed explanation to the Figure legend:

\textit{Red arrows indicate that the relative skill score deteriorated when moving from the natural to the log scale, green arrows indicate they improved.}

\red
The WIS contribution decomposition suggests that an alternative baseline should be used based on differences in transformed data rather than differences in natural scale data. Or, alternatively, that the a value is too low to give reasonable comparisons (as data that is hard/impossible to distinguish from 0 on a plot on the natural scale corresponds with very high penalization of forecasts considering 0 as a possibility). This could (also) be noted in Figure SI.5’s caption.

\black
I'm not entirely sure I understand the comment. Ideas, anyone?

\red
L340: “convert [...] rate” — Please clarify. Does “multiplicative growth rate” refer to a setup with $\mathbb{E}[X_{t+k} | X_t] = X_t \theta^k$, or only a single step $\mathbb{E}[X_{t+\text{one step}} | X_t] = X_t \theta^k$? Does the proposed conversion apply to both, or only to the latter?

@@

L341–342: “natural logarithm as a [. . . ] (VST)” — for what type of relevant distribution(s)?

L344: “take differences between forecasts on the log scale” — Clarify.

L345: “divide each forecast by the forecast” — Caveat about current forecast formats should be included here / in following sentences, without (one mention of) the idea about directly soliciting forecasts of week-on-week ratios in between.

\black
We updated the paragraph which now reads:

Johannes is that first sentence correct?

\textit{We suggested using the natural logarithm as a variance-stabilising transformation (VST) for variables that are approximately normally distributed and have a quadratic mean-variance relationship with $\sigma^2 = c \times \mu^2$ (this is e.g. approximately true for the negative binomoial distribution and large $\mu$, or alternatively the square-root transformation in the case of a Poisson distributed variable. Other VST like the Box-Cox (Box and Cox, 1964) are conceivable as well.
If one is interested in multiplicative, rather than exponential growth rates, one could convert forecasts into forecasts for the multiplicative growth rate by dividing numbers by the last value that was observed at the time the forecast was made. Forecasters would then implicitly predict a separate multiplicative growth rate from today to horizon 1, 2, etc. 
Instead of dividing by the last observed value, another promising transformation would be to divide each forecast by the forecast of the previous week (and analogously for observations), in order to obtain forecasts for week-to-week growth rates. Alternatively, one could also take first differences of values on the log scale. This approach would be akin to evaluating the shape of the predicted trajectory against the shape of the observed trajectory for a different approach to evaluating the shape of a forecast, see Srivastava et al., 2022). Dividing values by the previous value, unfortunately, is not feasible under the current quantile-based format of the Forecast Hubs, as the growth rate of the $\alpha$-quantile may be different from the $\alpha$-quantile of the growth-rate. However, it may be an interesting approach if predictive samples are available or if quantiles for weekwise growth rates have been collected. It is possible to go beyond choosing a single transformation by constructing composite scores as a weighted sum of scores based on different transformations. This would make it possible to create custom scores and allow forecast consumers to assign explicit weights to different qualities of the forecasts they might care about.
}

\blue
L366: “[...] settings” — (to standardize between measurements, then
could potentially scale by importance to stakeholders)

\black
We slightly adapted a sentence in the previous paragraph to make this point clearer:

\textit{It is possible to go beyond choosing a single transformation by constructing composite scores as a weighted sum of scores based on different transformations (potentially after standardising different scores to have the same mean and standard deviation). This would make it possible to create custom scores and allow forecast consumers to choose and assign explicit weights to different qualities of the forecasts they might care about.}

\textbf{Johannes, the standardising different scores thing should be kosher, right?}

\red
Figure SI.2: Would benefit from some more discussion, and perhaps a plot of slightly different quantities. E.g., to select an appropriate value of a, it seems like a common goal would be to deprioritize errors around values of x low enough that we expect there to be primarily noise rather than signal or that are not of concern to policymakers. For count data, this likely includes the values 0 - -10 in any circumstances; how far beyond 10 this range extends depends on the range of realistic growth rates, the forecast horizon, and cleanliness of the data. To assist in this decision, it seems like a similar plot of the evaluations of a particular absolute and/or relative error might be useful, or discussion of how to read it from the current plot. E.g., to illustrate that the same relative error is penalized roughly the same for all the plotted values of a for values of x above 50, but quite differently for $a = 10$ vs. $a = 0.1$ for values of x near 1.

\black
I'm not sure I can follow. In my mind the plot is there to show you that once your values are like 5 times larger than the offset you choose than the offset doesn't have much of an effect. So it's designed to show that for most practical purposes, doing log(x + a) should be mostly equivalent to log(x). So to me it's less about choosing an appropriate a and more about showing that probably it's just fine to go with some random small a. I think Figure SI.7 is more about "choosing an a".

\red
Figure SI.7:
\begin{itemize}
    \blue
    \item Also specify sorting variable\&direction on x axis. (Would a point plot vs. the sorting variable be more informative?)
    \red
    \item Very informative figure, promote to main text? Also would like to see for different “parts” of an epidemic (e.g., steady low periods, increases, peaks/plateaus, decreases). Deaths figures suggest that balancing scores between locations can be tricky, and both cases and deaths suggests that the investigated transformations can’t do this exactly.
\end{itemize}

\black
We added a statement to the legend "Locations are sorted according to the mean observed value in that location."

Thoughts on making this a main figure?

I would expect that one could find a value for a (e.g. 10?) that would eventually yield a more or less flat line.

\blue
\subsubsection{Typographical}
\blue
L96: “transformtation” $\xrightarrow{}$ “transformation”

@@

Figure 5: “Loaction” → “Location”

Figure SI.7: “Loaction” → “Location”

\black
Thank you very much for pointing these errors out. We have corrected them.

\red
In several places, e.g., L201, there are links to SI material, when clicked, that instead redirect to main text figures.

\black
Not sure why this happens - some Latex error? But also not sure worth fixing as they will do that anyway.

\red
\section{Reviewer \#3}

\blue
In this manuscript the authors investigate how common scoring rules for probabilistic forecasts can be adjusted by transforming observed data and forecast predictions prior to scoring. They provide three clear motivations for applying such transformations prior to scoring, assess the implications of different transformations in great detail, and evaluate the effects of these transformations using real-world COVID-19 forecasts obtained from the European Forecast Hub. Approaches that can help us improve how we measure the utility of epidemic forecasts for decision-makers are definitely needed. This is a very nice and timely contribution to epidemic forecast evaluation, and I only have a few comments.

\black
Thank you very much

@@

\blue
1. Line 96, typo: "log-transformtation".

\black
We corrected the typo

\blue
2. Figure 3: out of curiosity, do the rankings of forecasts A and B first switch at the same observed value (somewhere around 7?) in both panels? Zooming in, it looks as though maybe the switch occurs very slightly earlier for the log-transformed scoring.

\black
On the natural scale, the switch happens between 6.5 and 6.6 and on the log scale between 6.2 and 6.3.

\blue
3. Section 3.2, page 9: remarks concerning Figure 4 refer to months (e.g., May, July) but it's a little difficult to relate them to the figure, because the x-axis only has 6-month breaks and spans two years, so it isn't immediately apparent which year (or both?) the reader should focus on. That being said, it's great to see how the log-transformation yields similar scores when the forecasts miss peaks and troughs.

\black
That's a good point, we made the references in the text clearer and added years.

@@

\blue
4. Line 281: missing closing parenthesis, "(or $\beta_{\sqrt{}} = 0$, respectively".

\black
We corrected the typo

\blue
5. Figure 7: I can appreciate that the correlation between the natural and logarithmic scores decreases over the forecast horizon, as the absolute forecast error grows. But I found panel B more challenging to interpret. I gather the key message is that model rankings are quite consistent between the natural and log scales (panel A) even though the absolute scores differ markedly between the two scales — an effect that increases over the forecast horizon (panel B). Perhaps adding a sentence to this effect in the accompanying text (lines 292-295) would help other readers to avoid my confusion.

\black
We adapted the text and hopefully made it more clear:

For \textit{individual} forecasts, rankings between models for single forecasts are mostly preserved, with differences increasing across forecast horizons (see Figure \ref{fig:HUB-cors}A). While rankings between forecasters remain similar for a single forecast, this is not true anymore when looking at rankings obtained after averaging scores across multiple forecasts made at different times or in different locations. As discussed earlier, scores on the natural and on the log scale penalise errors very differently, e.g. when looking at performance during peaks or troughs. When evaluating performance \textit{averaged across} different forecasts and forecast targets, relative skill scores of the models therefore change considerably.

@@

\blue
6. Line 296, typo: "Figure Figure 8 shows ...".

\black
We corrected the typo

\blue
7. Section 3.4, page 14 and Figure 8: it's a welcome outcome that the Hub ensemble forecast remained the top model, given that the log-transformation clearly affects the individual model rankings. Presumably it would be reasonable to expect that ensemble forecasts for other regions, pathogens, etc, should be the best (or near-best) model when using log-transformed case counts?

\black
While more research is needed to conclude this with more confidence, we generally agree with the statement. We would also expect ensemble forecasts to do well (as they have done in the post) regardless of whether they are evaluated on the log or on the natural scale.

\blue
8. Lines 327-329: "A potential downside is that forecast evaluation is unreliable in situations where observed values are zero or very small."

@@

I feel there's an argument to be made here that rather than being a potential limitations, it could be considered an accurate reflection of the inherent uncertainty about the future course of an epidemic when case numbers are very small. This transformation also provides a valuable benefit in these situations, as the authors note a few sentences later: "It also gives higher weight to another type of situation one may care about, namely one in which numbers start to rise from a previously low level". This neatly illustrates the importance (as highlighted by the authors in this manuscript) of using multiple scoring rules to evaluate and compare forecasts.

\black
We added a sentence:

One could argue that this correctly reflect inherent uncertainty about the future course of an epidemic when numbers are small. Users nevertheless need to be aware that this can pose issues in practice.

\blue

@@

9. Table SI.2, "Criteria for removing forecasts": forecasts were removed if their median prediction differed greatly from the true value. This should probably be mentioned in the manuscript text, somewhere around line 235 (where Table SI.2 is referenced), to notify the reader that the definition of "erroneous forecasts" includes forecasts that are in extremely poor agreement with the ground truth. Otherwise, I feel that "erroneous" may be open to misinterpretation (e.g., only removing forecasts that predicted negative counts, NaN values, etc).

\black
This is a good point. We changed the sentence to

In addition, we filtered out erroneous forecasts that were in extremely poor agreement with the observed data, as defined by any of the conditions listed in Table SI.2.

### 2023-06-06 reply_to_reviews.tex

“For example, some methods of ‘scoring’ probabilistic predictions can be ‘gamed’ in the sense that forecasters can do better by reporting a probability distribution different to their best estimate. A proper scoring rule ensures that the expected score when reporting a distribution Q, as evaluated under their actual best estimate of the probability distribution P, is best when Q = P. Thus a proper scoring rule encourages a forecaster to provide ‘honest’ predictions."

In addition, I suspect there are a few readers (such as myself!) who are more familiar with more ‘basic’ scores such as e.g. logarithmic score or arise (i.e. essentially the likelihood or related quantities). I spent a bit of time wondering about why these weren’t considered, especially as these avoid the scale issues at the centre of the present article. Such scores were only briefly considered in the discussion, in the second-to-last paragraph. I think it would be helpful to mention/emphasise up front some of these ‘classic’ scores that don’t have the same issues with scaling and then discuss why they aren’t used, e.g. due to ‘robustness’ or other issues (e.g. lack of full probability distributions from forecasts).

\black
The paragraph now reads:

Proper scoring rules are constructed such that they cannot be gamed, meaning that forecasters (anyone or anything that issues a forecast) are incentivised to report their true belief about the future. In expectation, a forecaster receives the best score if their forecast $F$ coincides with the data-generating distribution $G$, that is if $F = G$. Common proper scoring rules are the logarithmic or log score \citep{goodRationalDecisions1952} or the continuous ranked probability score~\citep[CRPS,][]{gneitingStrictlyProperScoring2007}. The log score is the log-likelihood of the predictive density at the observed value and is scale-invariant under monotonous transformations. The log score does not suffer from the issues we address in this paper, but due to a number of reasons is not as widely used in fields such as weather forecasting or epidemiology (see e.g., \citealt{Johansson2019} for an exception). For example, the log score assigns particularly severe penalties to occasional misguided forecasts. This lack of robustness may limit its practical applicability \cite{bracherEvaluatingEpidemicForecasts2021}. Moreover, it is not easily applied to forecasts reported as samples or quantiles, as used in many recent disease forecasting efforts. 
For these reasons, the CRPS or its discrete equivalent, the ranked probability score~\citep[RPS,][]{funkAssessingPerformanceRealtime2019}, and the weighted interval score ~\citep[WIS,][]{bracherEvaluatingEpidemicForecasts2021} are more commonly used in epidemiology.

@@

\red
\subsubsection{Log vs other transformations}
The authors take the position that the log transformation is generally preferable for their use case, though they discuss and compare others. Relatedly, their arguments in terms of relative error also involve an essentially log-linear (i.e. log data + additive error) form which may be pragmatic but somewhat inelegant imo.

\black
ideas? Maybe we can just respond to this and the next one together.

Otherwise suggestion nikos: 
In the manuscript we simplify the equations a little bit by looking at the case of a single point forecast, rather than a probabilistic forecast that comes in the form of a predictive distribution. We feel this makes the discussion more intuitive. We want to emphasise that the log-linear error is really the error that is measured by the score, not the error model that would be assumed by any forecaster making a prediction.

\blue
As the authors note, a particularly controversial issue for the log transformation is the issue of zero values. They take the standard pragmatic stance that we can use log (eps + y) instead of log y in such cases. Many communities e.g. econometrics are vehemently opposed to this, preferring e.g. quasi-Poisson regression and robust standard errors in the context of estimation. While not completely opposed to log (eps + y) myself (I have used it too!) it makes me a bit uncomfortable I still can’t help but feel that something along the lines of e.g. logarithmic/quasi-likelihood or deviance scores could be formulated that would be preferable to the log data transform. This would offer both automatic scaling and handling of zero values, in principle. However, I haven’t thought carefully enough to offer a concrete alternative and the log(eps + y) approach appears to work reasonably here. Instead, and in combination with the previous point, perhaps a bit more discussion of the potential alternatives based on quasi-likelihood-style functions rather than data transformations could be added?

\black
Thank you for raising this interesting point. We have refered to the log score in our manuscript as a score that is scale invariant under monotonic transformations and mention in the discussion that for the log score the question of which scale to evaluate forecasts on does not arise. We feel that the ideas based on quasi-likelihood require more investigation and are beyond the scope of this paper.

@@

\red
\subsubsection{Observation and process models}
The interpretation in e.g. 2.2 appears to essentially assume a deterministic process model and additive error on the log scale (multiplicative on the natural scale). Although more of a motivating heuristic than strict assumption, a deterministic process model based on a mean will not in general be the same as a stochastic process model, right? Perhaps a further caveat that this is a fairly simplistic motivating tool might be useful?

Furthermore, why not assume that the model mean (say the output of the deterministic model) defines e.g. the mean of something like a Poisson distribution (probably in overdispersed/quasi form)? or negative binomial? The potential use of these distributions is considered in later sections in the context of motivating variance transforms, but then would again seem to motivate a (quasi-)likelihood-style score beyond the approximate transforms (though with pros and cons in terms of robustness, applicability in the presence of partial information).

\black
It is important to note that the equations in 2.2 do not refer to any particular model used by a forecaster or any model that was fit to data. Rather, we define the instantaneous growth rate for a single realised epidemic and then show that scoring forecasts for that on the log scale equates to scoring a forecast of the average growth rate according to this definition. The forecaster themselves who would make a forecast could assume any error model or model structure they like.

@@

\blue
I think the term ‘propriety’ (as in having the property of being proper) should either be explicitly defined or re-worded in terms of ‘being proper’.

\black
We reworded occurences of the term `propriety'.

\red
No reference is provided for the approximate variance-stabilising properties of the square root transformation.

\black
We added a reference to the following book:  \url{https://www.google.fr/books/edition/Generalized_Linear_Models_With_Examples/tBh5DwAAQBAJ?hl=en&gbpv=1&dq=variance-stabilizing+transformation+square+root&pg=PA119&printsec=frontcover}, page 118

@@

\red
\section{Reviewer \#2}

\textbf{Summary}

This manuscript develops theory, interpretations, and intuition regarding evaluation metrics applied to strictly monotonic transformations of observations and forecasts, with focus on log, shifted log, sqrt, and shifted sqrt transformations, and details the application and impact of using a log1p transformation within an evaluation framework for COVID-19 forecasts.
The analysis is extensive and covers many facets of selecting and applying such transformations, providing great value. However, it
\begin{itemize}
    \item focuses on putting evaluations for different locations and times on an even scale, and does not directly answer the question of how to re-emphasize locations and times of import to forecast consumers, and
    \item the discussion of which locations and times forecasts consumers would want to emphasize seems incomplete.
\end{itemize}
The former point could be addressed by adding additional content regarding re-emphasis. The latter point could be addressed by studying what stakeholders want to emphasize and using that to make a recommendation for a particular transformation or transformation selection rule. Alternatively, both could be addressed simply by more explicitly and prominently noting that
\begin{itemize}
    \item when selecting a transformation, one should consider the desired emphasis, which is likely not an even scale for most/all predictions, and
    \item the “natural logarithm” / log1p selection is not meant as a recommendation but to enable demonstration.
\end{itemize}

We added the following to the discussion to make our intentions clearer regarding the preferences of policy makers: 
\textit{In this paper, we did not make any particular assumptions about policy makers' priorities and preferences. Rather, we aimed to enable users to make an informed choice by showing how different transformations lead to different relative weights for the kinds of prediction errors forecast consumers may care about, such as absolute vs. relative errors or the size of penalties for over- vs. underprediction. In practice, engagement with decision makers is important to determine what their priorities are and how different ways to measure predictive importance should be weighed.}

It is important, however, that changing the relative weight for different times and locations is one effect of the scoring forecasts on the log scale, but not necessarily the main point of the transformation. Rather, we do recommend to use evaluate forecasts on the log scale (in addition to the natural scale) as we believe the interpretation as a score of the exponential growth rather is meaningful in an epidemiological context.

Users who are explicitly concerned about the relative weights of different times and locations can e.g. find information in Figure SI.7 where we show what happens for different offsets. A user could e.g. choose an offset such that the desired weights would result for different locations / times.

@@

\black
L20 refers to the abstract. I changed ``Applying the log transformation'' to ``Applying a transformation of log($x + 1$)''.

In a more principled sense I'm not sure overloading the terminology is that much of a problem, since we explicitly analyse that adding 1 doesn't make that much of difference. We could make it more explicit though.

\red
L18:
\begin{itemize}
    \item ``relative error'' --- Is this what stakeholders want? Or does it overemphasize low steady periods too much?
    \item ``under the assumption of quadratic mean-variance relationship'' --- And do we expect/observe this sort of relationship in epidemiological surveillance data? This reads more like an arbitrary assumption that will be taken instead of something that is examined in the manuscript. (From Section 3.3 it seems like the answer is ``roughly but not entirely''.)
    \item These points might be more simply resolved simply by revising L15 ``motivate''.
\end{itemize}
\black

The sentence in the abstract now reads: 
\textit{Using the CRPS on log-transformed values as an example, we list three attractive properties:}

relative error is one option that could be interesting. 
Johannes: e.g., \url{https://www.pnas.org/doi/pdf/10.1073/pnas.2103302119} emphasizes that the use of MAPE is motivated by its
straightforward interpretation. 
Ultimately stakeholders need to decide for themselves what they want. 
Can we find another example?

Quadratic mean-variance relationship means: we can forecast the growth rate equally well regardless of the observed magnitude at the moment. It's a straightforward motivation.

@@

\red
Figure 3: is a geometric distribution realistic for epidemiological surveillance data?

\black
Nikos: Again refer to Akira's paper?

Johannes: Agree that it is not. Could add something along the lines of ``this can happen in principle, but only in rather constructed cases, such as for the geometric distribution in Fig 3, which is unlikely to occur in an epi setting.

\blue
L236: “better able to illustrate the effects” — Why does this removal help illustrate the effects? Is such a removal procedure required to be able to apply this transformation approach at all? And if so, what are the requirements/considerations for such a removal procedure?

@@

\black
We updated the paragraph as follows:

\textit{In addition, we filtered out erroneous forecasts that were in extremely poor agreement with the observed data, as defined by any of the conditions listed in Table \ref{tab:erroneous}. Figure \ref{fig:erroneous-forecasts.png} shows the percentage of forecasts removed for each model. Those few (less than 0.2\%  of forecasts for each model) erroneous outlier forecasts had excessive influence on average scores and relative skill scores in a way that was not representative of normal model behaviour. We removed them here in order to better illustrate the effects of the log-transformation on scores that one would expect in a 'normal' scenario. In a regular forecast evaluation such erroneous forecasts should usually not be removed and would count towards overall model scores.}

@@

\black
I'm not sure where we should note this. This is already more or less the beginning of the example part. 
And for the theoretical part it's not that relevant, because missingness is somewhat independent of whether we transform forecasts.

We could add a sentence like "This transformation approach can be combined with approaches like pairwise comparisons that handle missingness"? earlier in the introduction?

\red
Figure 4: The data (not) selected seems to obscure the key period of predicting the start of a case wave, as we expect the CRPS of log data to emphasize missed case increase predictions there more heavily than the natural scale. Deaths are not a substitute because they have access to a leading indicator and the same sort of misses may not be observed. The evaluations here may also miss some overshooting of the case peak. Which rules from Table SI.2 are coming into play and why? Is there a more complete alternative example?

\black
The data that was removed here was largely due to data revisions, not due to forecasts removed by the filtering. 
We added the percentages of observed values in the main text and added the following two Figures in the SI to make that clearer.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.49\textwidth]{output/figures/number-anomalies.png}
     \includegraphics[width=0.49\textwidth]{output/figures/erroneous-forecasts.png}
     \caption{}
    \label{fig:number-anomalies}
\end{figure}

@@

\blue
L23–L24 “more strongly emphasized”, “less severely penalized” — Could note that this is relative to evaluations on the natural scale (not relative to each other).

\black
Thank you for the suggestion. We updated the abstract as such:

\textit{Situations in which models missed the beginning of upward swings are more strongly emphasised while failing to predict a downturn following a peak is less severely penalised when scoring transformed forecasts as opposed to untransformed ones.}

\blue
L24 “is only one” — Seems a bit too similar to “the only one”, “the only”, etc.

@@

\black
We hope that the remainder makes it sufficiently clear that other transformations are possible.

\blue
L46 “WIS is an approximation of the CRPS” — Is it an approximation of CRPS itself or some (2x?) scaling?

\black
The weighted interval score is a weighted sum of interval scores for the individual prediction intervals. When weighing the individual interval scores for the central $1 - \alpha$ prediction intervals by 
$w = \alpha / 2$ (which is generally standard), then the WIS converges exactly to the CRPS for an increasing number of equally spaced prediction intervals. 
\textbf{Proper scoring rule dragon, attack!} JB: No scaling. See figure 2 in \cite{bracherEvaluatingEpidemicForecasts2021}.

@@

\red
L69: This might benefit from a short justification (e.g.,
$\left| \frac{x_t e^{(r_t + \epsilon) \Delta t} - x_t e^{r_t \Delta t}}{x_t e^{(r_t - \epsilon) \Delta t} - x_t e^{r_t \Delta t}} \right| = e^{\epsilon\Delta t}$)

\black
Do we want to add this?

\red
L70: Clarify: is this suggesting to make the forecasting targets themselves the result of applying some standardized growth rate estimator to current+future observations around the desired time period?

\black 
I am confused...
I think what we want to say is that it would be preferable to evaluate a forecast on the growth rate if one were available. Luckily, we can do that by using a log transformation.

Say that we have something in the discussion that suggests transforming to growth rates directly.

\red
L99: How are atoms at $\exp x = 0$ handled? How are observations of $y = 0$ handled?

\black
In this theoretical discussion we defined prediction targets to have strictly positive support, so these cases are excluded. In the later parts we follow the common strategy to add an offset before taking the logarithm.

@@

\black
thoughts?

\red

L158 “delta method” — Delta method would seem to also require the distribution to be somewhat tightly distributed, concentrated within a nearly-linear region of the transformation function. But putting significant mass on a wider range of values would also mean having non-negligible mass on negative values if “approximately normal”; it would not make sense to apply the logarithm or sqrt transformations in these cases. So perhaps the “tightly distributed” assumption can be taken. But this seems a bit nonobvious and a justification/application of the delta method would be helpful here.

\black
thoughts?

\red
JB: This argument is a standard justification for the choice of variance-stabilizing transformations, see e.g., the below excerpt from \textit{Generalized Linear Models With Examples in R} by Dunn and Smyth:
\begin{quote}
Suppose that $y$ has a mean-variance relationship defined by the function $V(\mu)$, with $\text{var}(y) = \phi V(\mu)$. Then, consider a transformation $y^* = h(y) \approx h(\mu) + h'(\mu)(y - \mu)$, from which it can be inferred that
$$
\text{var}(y^*) = \text{var}[h(y)] \approx h'(\mu)^2\text{var}(y).
$$
Hence, the transformation $y^* = h(y)$ will approximately stabilize the variance if $h'(\mu)$ is proportional to $\text{var}(y)^{-1/2} = V(\mu)^{-1/2}$. When $V(\mu) = \mu^2$ [...], the variance-stabilizing transformation is the logarithm, because then $h'(\mu) = 1/\mu$.  When $V(\mu) = \mu$, the variance-stabilizing transformation is the square root because $h'(\mu) = 1/\mu^{1/2}$.
\end{quote}

STILL NEED TO ADD THAT REMARK
We added a reference to this source. We nonetheless agree with the referee that this approximation will work best if the distribution is tight and added a short remark to this regard.

\red
L159 — Need to discuss / spell out the point of the above calculation (— that it is the same for all $\mu$, when paired with the same $c$?).

\black
Not sure I understand this.

@@

\blue
L168: “grows with the variance” — May read like this a linear growth. Consider “grows with the standard deviation”.

\black
We have modified the sentence, which now reads:

\textit{We see that when applying the CRPS on the natural scale, the expected CRPS grows monotonically as the variance of the predictive distribution (which is equal to the data-generating distribution for the ideal forecaster) increases.}

@@

\black
In this instance "data-generating" is correct, as this is about a general property of proper scoring rules. We changed the sentence slightly to make this clearer:

\textit{We computed expected CRPS values  for three different distributions, assuming an ideal forecaster with predictive distribution equal to the true underlying (data-generating) distribution.}

\red
L186: “incentivizes overconfident predictions” — Needs justifica- tion/citation/removal. This single example disproves propriety but doesn’t establish overconfidence as being encouraged in general.

\black
While not proved here this is a statement that holds generally. Johaaannes? Also maybe we need a reference for this... JB: I am not actually sure about this -- may need to remove.

@@

\textit{Red arrows indicate that the relative skill score deteriorated when moving from the natural to the log scale, green arrows indicate they improved.}

\red
The WIS contribution decomposition suggests that an alternative baseline should be used based on differences in transformed data rather than differences in natural scale data. Or, alternatively, that the a value is too low to give reasonable comparisons (as data that is hard/impossible to distinguish from 0 on a plot on the natural scale corresponds with very high penalization of forecasts considering 0 as a possibility). This could (also) be noted in Figure SI.5’s caption.

\black
I'm not entirely sure I understand the comment. Ideas, anyone?

\blue
L340: “convert [...] rate” — Please clarify. Does “multiplicative growth rate” refer to a setup with $\mathbb{E}[X_{t+k} | X_t] = X_t \theta^k$, or only a single step $\mathbb{E}[X_{t+\text{one step}} | X_t] = X_t \theta^k$? Does the proposed conversion apply to both, or only to the latter?

\red
L341–342: “natural logarithm as a [. . . ] (VST)” — for what type of relevant distribution(s)?

\blue
L344: “take differences between forecasts on the log scale” — Clarify.

@@

L345: “divide each forecast by the forecast” — Caveat about current forecast formats should be included here / in following sentences, without (one mention of) the idea about directly soliciting forecasts of week-on-week ratios in between.

\black
We updated the paragraph which now reads:

Johannes is that first sentence correct?

\textit{We suggested using the natural logarithm as a variance-stabilising transformation (VST). This is appropriate for variables that are approximately normally distributed and have a quadratic mean-variance relationship with $\sigma^2 = c \times \mu^2$ (this is e.g. approximately true for the negative binomoial distribution and large $\mu$.

### 2023-06-06 reply_to_reviews.tex

or alternatively the square-root transformation in the case of a Poisson distributed variable. Other VST like the Box-Cox (Box and Cox, 1964) are conceivable as well.
If one is interested in multiplicative, rather than exponential growth rates, one could convert forecasts into forecasts for the multiplicative growth rate by dividing numbers by the last value that was observed at the time the forecast was made. Forecasters would then implicitly predict a separate multiplicative growth rate from today to horizon 1, 2, etc. 
Instead of dividing by the last observed value, another promising transformation would be to divide each forecast by the forecast of the previous week (and analogously for observations), in order to obtain forecasts for week-to-week growth rates. Alternatively, one could also take first differences of values on the log scale. This approach would be akin to evaluating the shape of the predicted trajectory against the shape of the observed trajectory for a different approach to evaluating the shape of a forecast, see Srivastava et al., 2022). Dividing values by the previous value, unfortunately, is not feasible under the current quantile-based format of the Forecast Hubs, as the growth rate of the $\alpha$-quantile may be different from the $\alpha$-quantile of the growth-rate. However, it may be an interesting approach if predictive samples are available or if quantiles for weekwise growth rates have been collected. It is possible to go beyond choosing a single transformation by constructing composite scores as a weighted sum of scores based on different transformations. This would make it possible to create custom scores and allow forecast consumers to assign explicit weights to different qualities of the forecasts they might care about.
}

@@

\blue
L366: “[...] settings” — (to standardize between measurements, then
could potentially scale by importance to stakeholders)

\black
We slightly adapted a sentence in the previous paragraph to make this point clearer:

\textit{It is possible to go beyond choosing a single transformation by constructing composite scores as a weighted sum of scores based on different transformations (potentially after standardising different scores to have the same mean and standard deviation). This would make it possible to create custom scores and allow forecast consumers to choose and assign explicit weights to different qualities of the forecasts they might care about.}

\textbf{Johannes, the standardising different scores thing should be kosher, right?} JB: not sure

@@

\blue

9. Table SI.2, "Criteria for removing forecasts": forecasts were removed if their median prediction differed greatly from the true value. This should probably be mentioned in the manuscript text, somewhere around line 235 (where Table SI.2 is referenced), to notify the reader that the definition of "erroneous forecasts" includes forecasts that are in extremely poor agreement with the ground truth. Otherwise, I feel that "erroneous" may be open to misinterpretation (e.g., only removing forecasts that predicted negative counts, NaN values, etc).

\black
This is a good point. We changed the sentence to

In addition, we filtered out a small number of erroneous forecasts that were in extremely poor agreement with the observed data, as defined by any of the conditions listed in Table SI.2.

\clearpage
\bibliography{log-or-not-v2.bib, software.bib}
